Recursive algorithm and branching for nonmaximal embeddings

### 2010-12-25 AffineLieAlgebras/InformalNotes/article.tex
Spelling
Figure 3 fixed, PDF regenerated.
List of changes is prepared.

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We study the modifications of the fan technique and demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan -- the tool that describes
  explicitly the recurrent properties of branching coefficients.
  Possible applications of fan technique in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ orthogonal to $\af$.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
to the injection $\frak{a} \rightarrow \frak{g} $.
The property is formulated in
terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebra of finite-dimensional or affine Lie algebra.
In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
becomes trivial
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
and the relations described earlier in \cite{ilyin812pbc} are reobtained.

@@

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

@@

Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
\af_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{eqnarray*}
The immediate consequence of this equality is:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\af}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
are subject to linear relations and the form of these relations changes
when the tested weight $\xi $ coincides with one of \ the ''singular
weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \frak{g}}$ and pass to a summation over the vectors of the
injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}

@@

Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
The root $\alpha_1$ is orthogonal to $\beta$,
so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
According to (\ref{fan-definition})
the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
where the second component is the value of the sign function $s(\gamma)$.
Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
are indicated by circles with the superscript $\epsilon\left( w \right)$.
The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
This means that singular weights located above the $\beta$-line
belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
We obtain four highest weights for $\af_{\perp }$-modules. In terms of
$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
$\left\{ \mu _{\af_{\perp }}\left( u\right)
=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
 are
$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
are attached to the set of $\af$-weights
$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
In fact we do not need the
weight diagrams but only the dimensions of modules
$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
has the set of weights with anomalous multiplicities:
\begin{equation}
  \label{eq:25}
  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
\end{equation}

@@

In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
\begin{eqnarray*}
  \label{eq:19}
  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
 \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
 \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
\end{eqnarray*}
The subalgebra $\af=B_2$ is fixed by the simple roots
\begin{equation*}
  \label{eq:26}
 S_{B_2}=\{e_3-e_4,e_4\}.
\end{equation*}
Its orthogonal counterpart $\afb=B_2$ has
\begin{eqnarray*}
  \label{eq:27}
  S_{\afb}=\{e_1-e_2,e_2\},\\
 \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
\end{eqnarray*}
As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6} -- \ref{fan-defined})).
As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
 $s\left(\gamma + \gamma_0\right)$.
The result is presented in Figure \ref{fig:B4B2Fan}.

@@

Using the defining relation (\ref{fan-defined}) we construct the
fan $\Gamma_{\hat A_1\to\hat A_2}$.
In this case $\gamma_0 =0$ its sign is minus, $s\left( 0 \right)=-1$, thus we are to use the
sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).

@@

Using (\ref{fan-defined}) we obtain the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
Values of the sign function $s(\gamma)$ for
$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10.eps}
  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

$\af \subset \gf$

>>>>

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan and the analogue of the Weyl numerator -- the tools that describe
  explicitly the recurrent properties of branching coefficients.
  Possible applications of fan technique in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ orthogonal to $\af$.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
to the injection $\frak{a} \rightarrow \frak{g} $.
The property is formulated in
terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebras of finite-dimensional or affine Lie algebras.
In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
becomes trivial
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
and the relations described earlier in \cite{ilyin812pbc} are reobtained.

@@

$\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

@@

Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
\af_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{eqnarray*}
The immediate consequence of this equality is:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\af}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
are subject to linear relations and the form of these relations changes
when the tested weight $\xi $ coincides with one of \ the ''singular
weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \frak{g}}$ and pass to a summation over the vectors of the
injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see Definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}

@@

Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
The root $\alpha_1$ is orthogonal to $\beta$,
so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
According to Definition \ref{fan-definition}
the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
where the second component is the value of the sign function $s(\gamma)$.
Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
are indicated by circles with the superscript $\epsilon\left( w \right)$.
The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
This means that singular weights located above the $\beta$-line
belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
We obtain four highest weights for $\af_{\perp }$-modules. In terms of
$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
$\left\{ \mu _{\af_{\perp }}\left( u\right)
=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
 are
$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
are attached to the set of $\af$-weights
$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
In fact we do not need the
weight diagrams but only the dimensions of modules
$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
has the set of weights with anomalous multiplicities:
\begin{equation}
  \label{eq:25}
  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
\end{equation}

@@

In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
\begin{eqnarray*}
  \label{eq:19}
  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
 \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
 \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
\end{eqnarray*}
The subalgebra $\af=B_2$ is fixed by the simple roots
\begin{equation*}
  \label{eq:26}
 S_{B_2}=\{e_3-e_4,e_4\}.
\end{equation*}
Its orthogonal counterpart $\afb=B_2$ has
\begin{eqnarray*}
  \label{eq:27}
  S_{\afb}=\{e_1-e_2,e_2\},\\
 \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
\end{eqnarray*}
As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
 $s\left(\gamma + \gamma_0\right)$.
The result is presented in Figure \ref{fig:B4B2Fan}.

@@

Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).

@@

Using Definition (\ref{fan-definition}) we obtain the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
Values of the sign function $s(\gamma)$ for
$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10.eps}
  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@
